A Constraint Solving Approach to Parikh Images of Regular Languages

### 2023-07-11 evaluation.tex
Grammarly

In \cref{fig:solve-division}, we show how many of the~\NrBenchmarks{} instances
the respective back-end could solve. A summary of their outcomes by instance
type is also available in \cref{tab:solve-status}. Note that many instances lack
a corum ground truth as they are solved by only one backend. We see that
\Calculus{} generally outperforms \Nuxmv{} on determining unsatisfiability, as
does baseline while being similar at satisfiable instances. Both \Calculus{} and
baseline outperforms baseline on satisfiable instances. On satisfiable
instances, \Nuxmv and \Calculus{} has similar performance.

@@

The most obvious threats to validity would be poor benchmarking or poor
implementation, e.g. if the method described in \cref{sec:calculus,sec:multiple}
deviate from what is actually benchmarked in section \cref{sec:experiments}, or
if the methods used for benchmarking would be unsound. To increase the
probability that our results are representative both in the sense of
representing  on expected inputs and in the statistical sense for a given run of
\Catra{} despite the use of randomness in our implementation we execute many
experiments. Moreover, to address the issue of correctness we have validated all
reported solutions made by \Calculus{} with \Nuxmv{} to ensure that \Calculus{}
is indeed sound. A previous version contained a race condition triggered by
random restarts during product materialisation which would in about
\numprint{0.7} of instances lead to non-deterministically unsound behaviour. We
have observed no instances of this bug or any other soundness issue since fixing
that bug, and have in addition to running all \NrBenchmarks{} we have
re-executed the same instances multiple times for long durations to capture
other soundness issues without any issue.

Another threat to validity would be if the competition (baseline and \Nuxmv)
would be disadvantaged in our comparison. For \Nuxmv{} we use the default
configuration which we believe should be performant (or it should not be the
default). Additionally, tweaking our invocation of \Nuxmv{} is explicitly made
easy for artefact reviewers. For baseline, our best argument is that the
solution we use is close to the one found in the \Ostrich{} string solver and
that it therefore should be realistic.

The greatest threat to validity remaining is our choice of implementation
platform and automata library. We There are some signs that product computation
is inefficient, notably the good performance of low-threshold automata
materialisation that prioritises computing smaller products. This means that
\Calculus{} makes less heavy use of product computation than baseline does,
instead relying more on \Princess{}. This situation would unfairly advantage
\Calculus{} if our automata library was the bottleneck due to our automata
library being unnaturally poor. We believe this is unlikely since similar
performance issues have been reported for string solvers. Additionally,
profiling suggests that both \Princess{}-based backends spend most of their time
in \Princess{}, suggesting that the automaton implementation is not the
bottleneck. Finally, we have compared aggregate results for both native backends
when optimising the automata construction procedures and observed that the trend
in performance differences has been robust as the automata library improved
vastly.

>>>>

In \cref{fig:solve-division}, we show how many of the~\NrBenchmarks{} instances
the respective back-end could solve. A summary of their outcomes by instance
type is also available in \cref{tab:solve-status}. Note that many instances lack
a corum ground truth as they are solved by only one backend. We see that
\Calculus{} generally outperforms \Nuxmv{} on determining unsatisfiability, as
does baseline, while being similar at satisfiable instances. Both \Calculus{} and
\Nuxmv outperforms baseline on satisfiable instances. On satisfiable
instances, \Nuxmv and \Calculus{} have similar performance.

@@

The most obvious threats to validity would be poor benchmarking or poor
implementation, e.g. if the method described in \cref{sec:calculus,sec:multiple}
deviate from what is actually benchmarked in section \cref{sec:experiments}, or
if the methods used for benchmarking were unsound. To increase the probability
that our results are representative both in the sense of representing expected
inputs and, in the statistical sense, for a given run of \Catra{} despite the
use of randomness in our implementation, we execute many experiments. Moreover,
to address the issue of correctness we have validated all reported solutions
made by \Calculus{} with \Nuxmv{} to ensure that \Calculus{} is indeed sound. A
previous version contained a race condition triggered by random restarts during
product materialisation which would in about \numprint{0.7} of instances lead to
non-deterministically unsound behaviour. We have observed no instances of this
bug or any other soundness issue since fixing that bug, and in addition to
running all \NrBenchmarks{}, we have re-executed the same instances multiple
times for long durations to capture other soundness issues without any issues.

Another threat to validity would be if the competition (baseline and \Nuxmv)
would be disadvantaged in our comparison. For \Nuxmv{}, we use the default
configuration, which we believe should be performant (or it should not be the
default). Additionally, tweaking our invocation of \Nuxmv{} is explicitly made
easy for artefact reviewers. For baseline, our best argument is that the
solution we use is close to the one found in the \Ostrich{} string solver and
that it, therefore, should be realistic.

The greatest threat to validity remaining is our choice of implementation
platform and automata library. There are some signs that product computation
is inefficient, notably the good performance of low-threshold automata
materialisation that prioritises computing smaller products. This means that
\Calculus{} makes less heavy use of product computation than baseline does,
instead relying more on \Princess{}. This situation would unfairly advantage
\Calculus{} if our automata library was the bottleneck due to our automata
library being unnaturally poor. We believe this is unlikely since similar
performance issues have been reported for string solvers. Additionally,
profiling suggests that both \Princess{}-based backends spend most of their time
in \Princess{}, suggesting that the automaton implementation is not the
bottleneck. Finally, we have compared aggregate results for both native backends
when optimising the automata construction procedures and observed that the trend
in performance differences has been robust as the automata library improved
vastly.
